Cosmological constraints from the redshift dependence of the distance rescaling in wrong cosmologies: the shape of galaxy 2-point correlation function

### 2016-08-18 draft/draft0.tex
updates

\shorttitle{Reshift Dependent Alcock-Paczynski effect from SDSS-III DR12}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}

@@

\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: application to the SDSS-III BOSS DR12 galaxies}

@@

\author{Xiao-Dong Li, Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park,}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
\author{David H. Weinberg,}
\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
\author{Donald P. Schneider,}
\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
University Park, PA 16802 }
\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\begin{abstract}
We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies and 
derive cosmological constraints from the redshift dependence of the Alcock-Paczynski (AP) effect.
The apparent anisotropy in the distribution of observed galaxies arise from two main sources,
the redshift-space distortion (RSD) effect due to the galaxy peculiar velocities,
and the geometric distortion when incorrect cosmological models are assumed for 
%the coordinate transformation from redshift space to comoving space, 
transforming redshift to comoving distance,
known as the AP effect.
%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters.
Anisotropies produced by the RSD effect are, although large,
maintaining a nearly uniform magnitude over a large range of redshift,
while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters 
%which is less sensitive to RSD contamination.
We split the DR12 galaxies into six redshift bins, measure the 2-point correlation function in each bin,
and assess the redshift evolution of anisotropies.
%Assuming a flat Universe consisting of a pressure-less dark matter component 
%with current ratio $\Omega_m$, and a dark energy component with constant equation of state $w$,
We obtain constraints of $\Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14$,
which are tighter than the current constraints from other cosmological probes
such as type Ia supernovae, cosmic microwave background, and baryon acoustic oscillation (BAO).
Combining these cosmological probes with our method yield tight constraints of 
$\Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03$.
Our method is complementary to the other large scale structure probes like BAO and topology.
%We discuss the caveats and possibilities for improving upon our methodology.
We expect this technique will play an important role in deriving cosmological constraints from
large scale structure surveys.
\end{abstract}

@@

The current standard model of cosmology has been highly successful at reproducing the Universe on large scales. %large scale observations of the Universe. 
From the temperature fluctuations in the cosmic microwave background (CMB), 
to the late time clustering of galaxies, 
the vacuum energy dominated cold dark matter model ($\Lambda$CDM) fits the data surprisingly well \citep{Planck2015,Anderson2013}. 
This result is all the more impressive considering both the underlying assumptions, 
such as homogeneity, isotropy, scale invariance of the primordial fluctuations, 
and the minimal set of cosmological parameters that are required.

Nonetheless, these models produce the unsatisfactory prospect that we must include within our ontology both a vacuum energy 
that is much smaller than that predicted from  quantum mechanics, 
or alternatively a new scalar field (dark energy) that has negative pressure
\citep{SW1989,Riess1998,Perl1999,PR2003,Li2011}, 
and a new matter component, which is not contained within the standard $SU(3)\times SU(2) \times U(1)$ formulation of particle physics.

With an over-abundance of models for both dark energy-like accelerated expansion and dark matter, 
it is crucial to obtain precise and model-independent measurements of the cosmic evolution, usually referred to as background observables. 
Two such observables are the angular diameter distance, $D_A$, and the Hubble factor, $H$.  
If these quantities can be measured at various redshifts and to a high degree of accuracy then our ability to differentiate between various competing models will be greatly increased.

In the last few years there has been increasing interest in using the Alcock-Paczynski (AP) effect \citep{AP1979} 
in the large-scale clustering of galaxies to obtain constraints on $D_A$ and $H$ \citep{Guzzo2008,topology}. 
Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
These distortions are induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

There have been several methods proposed for applying the AP test to the large scale structure (LSS).
The most widely adopted one uses anisotropic clustering \citep{Ballinger1996,Matsubara1996},
which has been used for the 2 degree Field Quasar Survey \citep{Outram2004},
the WiggleZ dark energy survey \citep{Blake2011}, 
the Sloan Digital Sky Survey-I/II (SDSS-I/II) Luminous Red Galaxy (LRG) survey \citep{Eisenstein et al. 2011,ChuangWang2012},
and the SDSS-III Baryon Oscillation Spectroscopic Survey (BOSS) 
%\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L}.
\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L,
Alam2016, Beutler2016, Sanchez2016}
The main caveat of this method is that,
because the radial distances of galaxies are inferred from redshifts,
AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
which leads to apparent anisotropy even if the adopted cosmology is correct.
The RSDs must be accurately modeled for the 2-point statistics of galaxy clustering.

\cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs.
Unfortunately this method is also seriously limited by RSD.
The peculiar velocity distorts the redshift and changes the apparent tilt angles of galaxy pairs.
The effect depends on both redshift and underlying cosmology, and is rather difficult to model accurately \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS
and requires large samples.

\cite{Li2014} proposed another method utilizing the redshift dependence of AP effect to overcome the RSD problem.
The anisotropies produced by RSD effect are, although very large,
close to uniform in magnitude over a large range of redshift.
Conversely, if cosmological parameters are incorrectly chosen, the LSS
appear anisotropic and the degree of anisotropy varies with redshift. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
%Thus we can focus on the redshift dependence of the galaxy density gradient field, 
%which is less affected by RSD, but still sensitive to cosmological parameters.
We used the {\it galaxy density gradient field} 
to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
demonstrating that the method leads to unbiased estimation of the density parameter $\Omega_m$ and the dark energy equation of state (EoS) $w$.

The same topic was revisited in \cite{Li2015}, but using the {\it galaxy two-point correlation function} (2pCF) as the statistical tool.
The 2pCF as a function of angle, $\xi(\mu)$, is measured at different redshifts.
Similar to \cite{Li2014}, we found that the RSD effect, although significantly distorting $\xi(\mu)$, 
exhibits much less redshift evolution compared to the amount of change in $\xi(\mu)$ due to incorrectly adopted cosmologies.
When incorrect cosmological parameters are adopted, 
the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
and the amplitude is shifted by the change in comoving volume;
both effects have significant redshift dependence.
%By focusing on the redshift dependence of $\xi(\mu)$, we can correctly recover the cosmological parameters despite the contamination of RSD.
We test the method using the 2pCF on mock surveys drawn from HR3
%we measuring the redshift evolution of 2pCF also leads to unbiased estimation of cosmological parameters 
and find the constraints obtained are tighter than those from the methodology of \cite{Li2014}.

The change of the comoving volume size is another consequence of an incorrectly adopted cosmology, 
and has motivated investigations constraining cosmological parameters from number counting of 
galaxy clusters \citep{PS1974,VL1996}. 
An obstacle in using the comoving volume for cosmological tests is the evolution of the number of target objects.
The essential need for reducing the evolution effects in applying the test led \cite{topology} to propose a new method
using the topology of LSS. 
Since the topology is a measure of intrinsic connectivity of structures,
it is expected to be insensitive to non-linear gravitational evolution, type of density tracers,
and RSD on large scales.
This method has been applied to the WiggleZ Dark Energy Survey data by \cite{WiggleZtopoloy},
and to simulated BOSS samples \citep{Speare2015}.

In this paper we apply our methodology to SDSS-III BOSS Data Release 12 (DR12) galaxies \citep{Reidetal:2016}.
%We split the DR12 samples of CMASS and LOWZ into six redshift bins (three in each) and measure the redshift evolution of 
%anisotropy therein to determine the correct cosmological parameters leading to least redshift evolution of anisotropy.
We take the 2pCF as statistical tool characterizing the anisotropic clustering and follow the procedure of \cite{Li2015} to conduct the analysis.
We assume a flat Universe and constrain parameters of $\Omega_m$ and $w$.
2pCF is a mature statistic in cosmology and its optimal estimation and statistical properties are well understood.
Compared with the density gradient field statistic, it leads to tighter constraints and is less affected by survey geometry.

The outline of this paper is as follows. 
In Sec. 2 we describe the observational data used in this paper.
In Sec. 3 we discuss the N-body simulations and mock galaxy catalogues that are used in this analysis.
In Sec. 4 we briefly review the nature and consequences of the AP effect when performing coordinate transforms in a cosmological context. 
In Sec. 5 and Sec. 6, we describe our analysis method and present the cosmological constraints obtained from BOSS DR12 galaxies. 
We conclude in Sec. 7.

@@

\section{The Observational Data}\label{sec:data}

The Sloan Digital Sky Survey (SDSS; York et al. 2000) %DANGEROUS
imaged approximately 7\,606 $\rm deg^2$
of the Northern Galactic Hemisphere and 
3\,172 $\rm deg^2$ of the Southern Galactic Hemisphere in the {\it ugriz} bands \citep{Fukugita1996,Gunn1998}.
The survey was performed using the 
2.5m Sloan telescope \citep{Gunn et al. 2006}
at the Apache Point Observatory in New Mexico.
%BOSS, as part of the SDSS-III survey \citep{Eisenstein et al. 2011},
%has obtained additional imaging,
%increasing the region of the south to 3\,172 $\rm deg^2$.
BOSS \citep{Dawson et al. 2012,Smee2013}, as a part of the SDSS-III survey \citep{Eisenstein et al. 2011},
has obtained spectra and redshifts 
of 1.37 million galaxies selected from the SDSS imaging,
covering a region of 9\,376 $\rm deg^2$.
The galaxy redshifts were measured by an automated pipeline \citep{Bolton2012}.

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowres.png}
   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowzlowres.png}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LN.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LS.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CN.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CS.jpg}
   \includegraphics[width=8.5cm]{fig1_0.eps}
   \includegraphics[width=8.5cm]{fig1_1.eps}
   \includegraphics[width=8.5cm]{fig1_2.eps}
   \includegraphics[width=8.5cm]{fig1_3.eps}
   }
   \caption{\label{fig_radec}
   The sky coverage of the LOWZ and CMASS samples in the north and south Galactic caps. 
   The individual points mark position of galaxies in the survey coordinate frame.
   The solid lines mark the right ascension and declination.
   The mean completeness is 97.2\% for the LOWZ sample, shown in the upper panels,
   and 98.8\% for the CMASS sample in the lower panels.
   The effective sky coverage is 8,337 $\rm deg^2$ for LOWZ and 9,376 $\rm deg^2$ for CMASS.
   %Each patch corresponds to a plate,
   %with the color determined by the completeness of that plate.
   See \cite{Reidetal:2016} for more details.
   }
\end{figure*}

The spectroscopic sample of BOSS has two primary catalogues.
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
The LOWZ sample is designed to extend the SDSS-I/II LRG sample to $z\approx 0.4$ and fainter luminosities,
in order to increase the number density of the sample by a factor of 3.
The CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$).
It was targeted to be an approximately stellar mass limited sample of massive, luminous galaxies.
The final data release (DR12) samples are described in \cite{Reidetal:2016},
where the details of targeting algorithms and the catalogues are provided.
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%Full details of targeting algorithms and the catalogues are provided in \citep{}, 
%and we do not replicate this here.

%The galaxy survey used two primary target algorithms, 
%selecting samples called LOWZ, with 361\,759 galaxies in the final data release DR12 \citep{dr12} between $0.15<z <0.43$ and CMASS, 
%with 771\,567 galaxies in DR12 between $0.43< z < 0.70$. 
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%which also shows that the samples jointly cover a large cosmic volume $V_{\rm eff}=7.4\,{\rm Gpc}^3$.
%with a number density of galaxies as a function of observed redshift, 
%that ensures that the shot noise does not dominate at BAO (baryon acoustic oscillation) scales. 
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%Full details of the catalogues are provided in \citet{Reidetal:2016}, 
%and we do not replicate this here.

%BOSS is designed to obtain 
%spectra and redshifts of $\sim$1.35 million galaxies 
%(together with 160\,000 quasars and approximately 100\,000 ancillary targets)
%selected from the SDSS imaging.
%The SDSS-I/II data \citep{York et al. 2000}

%CMASS and LOWZ\,

%We use data from the Sloan Digital Sky Survey \citep[SDSS; ][]{2000AJ....120.1579Y}. 
%SDSS has mapped over one quarter of the sky in five photometric bands down to a limiting magnitude of $r\sim 22.5$. 
%The photometric data is reduced and from it are selected targets for followup spectroscopy. 
%The spectroscopic survey, known as the Baryon Oscillation Spectroscopic Survey (BOSS), 
%is charged with obtaining spectra for 1.35 million galaxies over a 10,000 square degree footprint.

\begin{figure*}
   \centering{
   \includegraphics[width=19cm]{fig2.eps}
   }
   \caption{\label{fig_nbar}
      The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      The vertical dashed lines define the six redshift bins that are used to cut the samples.
      Their redshift ranges are listed.
      The number of LOWZ (CMASS) galaxies in the three low (high) redshift bins are presented in the brackets.
      }
\end{figure*}

Figure \ref{fig_radec} presents the sky coverage of the BOSS DR12 samples used in this analysis. 
%The light grey shaded region shows the expected total footprint of the BOSS survey. 
%Colors indicate the spectroscopic completeness.
The mean completeness is 97.2\% for the LOWZ sample, in the upper panels, and 98.8\% for the CMASS sample shown in the lower panels.
   %Each patch of different color corresponds to a plate,
   %with the color determined by the completeness of that plate..
Figure \ref{fig_nbar} shows the galaxy number density of the two samples.
In this analysis we use 361\,759 LOWZ galaxies at $0.15<z <0.43$ and 
771\,567 CMASS galaxies at $0.43< z < 0.693$.
%in total galaxies.
We split the galaxies into six redshift bins: 
three bins in LOWZ ($0.150<z_1<0.274<z_2<0.351<z_3<0.430$), 
and three in CMASS ($0.430<z_4<0.511<z_5<0.572<z_6<0.693$), 
as illustrated in Figure \ref{fig_nbar}.

\begin{figure*}
   \centering{
   \includegraphics[width=19cm]{fig3.eps}
   }
   \caption{\label{fig_mock}
      Creation of mock galaxy samples for BOSS.
      Using an all-sky mock survey from the HR4 or HR3 simulations,
       we are able to produce four sets of NGC samples or eight sets of SGC samples with non-overlapping sky coverage.
      The individual points are the right ascension and declination of 1\% galaxies drawn from the CMASS samples.
      }
\end{figure*}

Each spectroscopically observed galaxy is assigned several weights to account for observational effects. 
The galaxy weights are constructed from three distinct effects.
%redshift failure, $w_{fail}$, minimum variance, $w_{FKP}$, and angular variation, $w_{sys}$. 
%These weights are described in more detail in \cite{2012MNRAS.427.3435A} and \cite{2012MNRAS.424..564R}. 
Firstly, galaxies lacking a redshift due to fiber collisions 
\footnote{Fiber collisions occur when two objects are close enough together such that two fibers cannot be placed.
In BOSS, the collision radius is 62 $''$.}
or inadequate spectral information are accounted for by reweighting
the nearest galaxy by a weight $w_{\rm fail}=(1+n)$, 
where $n$ is the number of close neighbors without a measured redshift. 
Secondly, all galaxies are assigned `FKP' weights \citep{1994ApJ...426...23F}
%as a function of redshift depending on the number density.
as a function of number density,
to optimize the clustering measurements in the face of shot-noise and cosmic variance.
%according to,
%\begin{equation}
%w^i_{FKP}=\frac{1}{1+n_i(z)P_0},
%\end{equation}
%where $n_i(z)$ is the comoving space density at redshift $z$ and $P_0 \sim P(k=0.1~{\rm $h^{-1}$Mpc}) \sim 2\times 10^{4}h^{-3}{\rm Mpc^3}$, 
%as in \cite{2012MNRAS.427.3435A}. 
The third weight corrects for angular variations of survey completeness and the systematics 
related to the angular variations in stellar density that make detection of
galaxies difficult in over-crowded regions of the sky. %\citep{2012MNRAS.424..564R}. 
The total weight for each galaxy is the product of these three weights, $w_{\rm total}=w_{\rm fail}w_{\rm FKP}w_{\rm sys}$.

For the statistical analyses, 
random catalogues having the same angular and redshift selection functions as the data 
are provided along with the data \citep{Reidetal:2016}.
%Each random point is assigned with a redshift of measured galaxy randomly drawed from galaxies.
%and a weight given by the $w_{\rm tot}$ of the measured galaxy.
The random points are also weighted but they only include the minimum variance `FKP' weight. 
%50 times as many random points as we have galaxies

\section{The Mock Galaxy Data}
\label{sec:mocks}
%We use HR3 and HR4...
%We use HR4 J08 ...

%Shape of $\\xi$ measured in HR4 very similar to data...
%Shape of

For LSS studies mock survey samples created from simulations are crucial
for the correction of systematics and covariance estimation.
The Horizon Run simulations are a suite of large volume N-body simulations that 
have resolutions and volumes capable of accurately reproducing the observational statistics of the current major redshift surveys like 
SDSS-III BOSS \citep{park 2005,2009ApJ...701.1547K,horizonrun}.
The HR3 \citep{horizonrun} and HR4 \citep{hr4} simulations are used in our analysis.

From the HR3 and HR4 simulations we have generated all-sky light cone mock galaxy catalogues.
The all-sky spherical mocks are then incorporated with the same fiber collision effect, 
angular masks, and radial selection function with the real observational data,
creating mock surveys of BOSS DR12.

We impose a minimum mass limit varying along with redshift to match the radial density of BOSS samples.
The galaxies of the BOSS DR12 samples do not cleanly distribute above some particular mass boundary;
they always have a fuzzy, blur boundary extending to relatively small values (as an example, see Figure 3 of 
Parihar et al. 2014). %DANGEROUS
%rather than shaprly lying above a certain mass cut, 
Galaxies in the mock samples are systematically more massive than those from observations;
We will discuss the effect of this discrepancy in Sec. \ref{sec:caveats}.

\subsection{Horizon Run 4}

@@

%As will be introduced in the next section, 
The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
As shown in Figure \ref{fig_mock},
from one all-sky survey, 
we are able to create four sets of non-overlapping north Galactic cap (NGC) samples for CMASS and LOWZ, 
or eight sets of non-overlapping south Galactic cap (SGC) samples.
In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.
%We create four north

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig4_0.eps}
   \includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The redshift dependence of the AP effect in four incorrect cosmologies,
   assuming that the true cosmology is $\Omega_m=0.31$, $w=-1$.
   The left panel shows the apparent distortion of four perfect squares,
   measured by an observer located at the origin.
   The apparently distorted shapes are plotted in red solid lines.
   The underlying true shapes are indicated in blue dashed lines.
   The right panel displays the degree of the shape distortion, as described by Equations (\ref{eq:stretch}).
   The BOSS DR12 galaxies used in our analysis have a redshift coverage of $0.15 < z < 0.693$ (marked 
   by the gray vertical lines). Clearly, the magnitude of the shape distortion due to AP changes with redshift.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

\subsection{Horizon Run 3}
%In our analysis we also mock surveys constructed from one of the Horizon Run simulations, HR3.

As in HR4, HR3 also adopts a flat-space $\Lambda$CDM cosmology with the WMAP 5 year parameters.
The simulation was made in a cube of volume $(10.815\  h^{-1}{\rm{Gpc}})^3$
using $7120^3$ particles with particle mass of $1.25\times 10^{11}$\hMsun.
The simulations were integrated from $z=27$ and reached $z=0$ after making $N_{\rm step}=600$ global timesteps.
The collapsed high-density regions were identified using the Friend-of-Friend algorithm with the linking length of 0.2 times the mean particle separation.
The physically self-bound (PSB) subhalos that are gravitationally self-bound and tidally stable \citep{kim and park 2006} 
are identified and used as galaxy proxies.
The PSB halo finder is a group-finding algorithm which can efficiently identify halos located even in crowded regions. 
This method combines two physical criteria such as the tidal radius of a halo and the total energy of each particle to find member particles.
The group velocity of member particles is adopted as the peculiar velocity of each PSB subhalo.

%This provides a substantial increase in the similarity between simulation and observational data,
%as these dark matter subhalos are sites for galaxy formation.
%LRG (Xiao: is it OK to change all the ``LRG'' to ``galaxy''?) formation.

>>>>

\shorttitle{Reshift Dependent Volume effect}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}

@@

\title{Cosmological constraints from the redshift dependence of the distance rescaling in wrong cosmologies: 
the shape of galaxy 2-point correlation function}

@@

\author{Xiao-Dong Li, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cheng Cheng, }
\affil{blahblahblah}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park,}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\begin{abstract}
We use the shape of galaxy 2-point correlation function to measure the redshift dependence cosmology volume effect.
...
\end{abstract}

@@

Dark energy ... Large scale structure...

2pCF is a good statistic... blahblah
In 2d xi(s,mu) ...
In *** we used the redshift dependence of 2pCF to probe the volume and AP effect...
The method is applied to BOSS data in *** and obtain tight constraint...

In *** we further propose to use the shape of xi(s) to probe the volume effect...
Stretch or compression shifts the clustering properties in some particular scale to larger or smaller scales...
The shape of measured xi(s) is thus stretched or compressed.

The outline of this paper is as follows.

@@

This paper is organized as follows...
The outline of this paper proceeds as follows. 
In \S 2 we briefly review the nature and consequences of the AP effect and volume changes when performing coordinate transforms in a cosmological context. 
In \S 3 we describe the N-body simulations and mock galaxy catalogues that are used to test our methodology.
In \S 4, we describe our new analysis method for quantifying the redshift dependence of volume effect.
We conclude in \S 5.

\section{AP and Volume Effect in Wrongly Assumed Cosmologies}
\label{sec:Voleffect}

\begin{figure*}
   \centering{
%   \includegraphics[height=6cm]{Tpcf--xy.eps}
%   \includegraphics[height=6cm]{Tpcf--quan.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The redshift dependence of AP and volume effect in two wrongly assumed cosmologies $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$,
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Upper panel shows the apparent distortion of four perfect squares,
   measured by an observer located at the origin.
   The apparently distorted shapes are plotted in red solid lines.
   The underlying true shapes are plotted in blue dashed lines.
   Lower panel shows the evolution of Equations (\ref{eq:stretch}) and (\ref{eq:volume}).
   In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the AP and volume effect in wrongly assumed cosmologies.
A more detailed description of the AP effect has been provided in \cite{Li2014}.

Suppose that we are probing the shape and volume of an object in the Universe.
We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
then compute its sizes in the radial and transverse directions from the relations of 
\begin{equation}\label{eq:distance}
\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
\end{equation}
where $H$ is the Hubble parameter, $D_A$ is the angular diameter distance.
In the particular case of a flat universe with constant dark energy EoS, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
The degree of variations in shape and volume can be described by the following quantities
\begin{equation}\label{eq:stretch}
 %{\rm Degree\ of\ LOS\ stretch\equiv}
 %{\rm rat}_{\rm LOS\ stretch}\equiv
 \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
\end{equation}
\begin{equation}\label{eq:volume}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
 = \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
 = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and wrongly assumed cosmology.
From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.

The AP and volume effect due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xy}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute four perfect squares at various distances from 500 Mpc/h to 3,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
using redshift-distance relations of two incorrect cosmologies:
\begin{enumerate}
 \item $\Omega_m=0.41$, $w=-1.3$,
 \item $\Omega_m=0.11$, $w=-0.7$,
\end{enumerate}
the shapes of the squares appear distorted (AP effect),
and their volumes are changed (volume effect).
In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction (hereafter ``LOS shape stretch'')
and magnification of the volume (hereafter ``volume magnification''), 
while in the model with $\Omega_m=0.41$, $w=-1.3$, we see opposite effects of LOS shape compression and volume shrinkage.

In the lower panel of Figure \ref{fig_xy}, we plot the degree of variations in shape and volume as functions of redshift. 
In cosmology (i), both quantities have values less than 1, 
indicating LOS shape compression and volume shrink.
The effect in cosmology (ii) is slightly more subtle. At low redshift, the effect of dark energy is important, 
and there is LOS shape compression and volume reduction due to the quintessence like dark energy EoS.
However, at higher redshift the role of dark matter is more important, and we see LOS shape stretch and volume magnification due to the small $\Omega_m$.

More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP and volume effects. 
For example, in the cosmology with $\Omega_m=0.41$, $w=-1.3$, 
both the LOS shape stretch and volume magnification become more significant with increasing redshift.
In the cosmology with $\Omega_m=0.11$, $w=-0.7$,
not only do the magnitudes of the effects evolve with redshift,
but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.

\section{The Simulation Data}\label{sec:data}

@@

%As will be introduced in the next section, 
The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
As shown in \cite{bossAP},
from one all-sky survey, 
we are able to create four sets of non-overlapping north Galactic cap (NGC) samples for CMASS and LOWZ, 
or eight sets of non-overlapping south Galactic cap (SGC) samples.
In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.
